\documentclass[letterpaper,11pt]{article}
\usepackage{setspace}

%====== Packages ===================================
\usepackage{graphicx, xcolor, color}
\usepackage{booktabs}
\usepackage[colorlinks=true, urlcolor={violet}, citecolor={blue}, linkcolor={red}]{hyperref}
\usepackage{vmargin}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{natbib}
\usepackage{hyperref}
\hypersetup{%
  colorlinks = true,
  linkcolor  = black
}
%====== Set Margins ===================================
       \setpapersize{USletter}
       \setmarginsrb{1in}{0.5in}{1in}{.9in}{0in}{0.0in}{0.5in}{0.3in}
%====== Font===================================
\definecolor{deepred}{rgb}{0.61, 0.0, 0.14}
\definecolor{osugrey}{rgb}{0.405, 0.405, 0.405}

\renewcommand{\familydefault}{\sfdefault}
%\usepackage{cmbright}
%\usepackage{helvet}
%\usepackage{avant}
\usepackage{sectsty}
\sectionfont{\color{deepred}\Large\mdseries}
\subsectionfont{\color{deepred}\large\mdseries}
\subsubsectionfont{\color{deepred}\normalfont \mdseries}
%\allsectionsfont{\sffamily\underline}
%\sectionfont{\normalfont\sffamily\large\bfseries\color{deepred}\sectionrule{0pt}{??0pt}{-4pt}{1pt}}
\setcounter{secnumdepth}{0}

\newcommand{\compresslist}{%
\setlength{\itemsep}{1pt}%
\setlength{\parskip}{0pt}%
\setlength{\parsep}{0pt}%
}

%\fontsize{10.5}{12}\selectfont

%====== Startup ===================================
\begin{document}
%====== Title===================================
\newcommand{\rauthor}[1]{\noindent \large{\textcolor{deepred}{#1}}}
\newcommand{\rtitle}[1]{\noindent \textcolor{osugrey}{\huge{#1}} }
\thispagestyle{empty}
\vspace{-30pt}
\rtitle{Research Assistant Work}   

\hspace{-1cm}\textcolor{deepred}{\textbf{\Huge{\underline{\phantom{x} \hspace{7in} \phantom{x}}}}} \\

\rauthor{\Large{Skyler Cranmer Meeting}}\\
March 7, 2018\\

 \vspace{0.5cm}

\subsection*{Knockout Updates}
\begin{itemize}
\item I finished the data processing programs. 
\item Nate is trying for 07-08 April. 
\item Nate is going to email the squadrons again later this week if he does not hear back from them.
\item John is going to mail the tablet and computer back this week.  
\item This week I am going to build the t-test model and finish a random spot check algorithm. 
\end{itemize}

\subsection*{CHAMP}
\begin{itemize}
\item I made two output data frames that review the variables. There seem to be a few corrupted files, but they may be able to be fixed with regular expressions. 
\item Caleb is reviewing the output this week for a write up for Brice and you. I will help finish the write up once I finish some midterm projects. 
\end{itemize}

\subsection*{High Impact Projects}

\begin{enumerate}
\item Knockout; 
\item Rwandan genocide; 
\item Suicide vs standard soldier; 
\item CHAMP;
\item Project with Daniel on immigration vs trade;
\item Time series bombing on ISIS recruitment; 
\item Civil war alliances in different international systems. Do other theories about changing civil wars hold? (Future project.)
\end{enumerate}

\begin{itemize}
\item I finished coding the ISIS emails. I am writing programs to clean them. Bear wants us to write a PNAS style article for his class. I am going to meet with him to see if it is okay to write my ISIS paper up. 
\item I am going to start coding the Assad email data. I think it would be interesting to see how information flow is different in his government vs. Hillary Clinton's email flow. 
\item My project work with Erin Lin is finished. 
\item Starting an article with the Rwandan professors. 
\item Any update on the social network project that you were thinking of bringing me on? 
\end{itemize}


\end{document}